Reaction & action alternatives

### 2023-05-31 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/reaction_action_alternatives.Rmd
action alternatives

# correlation: count x quality 
```{r}

@@

# novices: correlation between count and quality
cor.test(corr.nov$count, corr.nov$nd, method=c("spearman"))

>>>>

# correlation: count x quality (sum score)
```{r}

@@

# novices: correlation between count and quality
cor.test(corr.nov$count, corr.nov$nd, method=c("pearson"))

# experts: correlation between count and quality
cor.test(corr.exp$count, corr.exp$nd, method=c("pearson"))

# correlation: count x quality (relative score)
```{r}

# novices: correlation between count and quality
cor.test(corr.nov$count, corr.nov$percent_nd, method=c("pearson"))

# experts: correlation between count and quality
cor.test(corr.exp$count, corr.exp$percent_nd, method=c("pearson"))
